\documentclass[a4paper,11pt]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{burgundy}
\usepackage[hmargin=1in, vmargin=1in]{geometry}

\usepackage{unicode-math}
\defaultfontfeatures{Mapping=tex-text,Ligatures={TeX,Common},Scale=MatchLowercase}
\defaultfontfeatures[\rmfamily]{Scale=1} % To scale all fonts correctly
\setmainfont{TeX Gyre Pagella}
\setmathfont{Asana Math}

\usepackage{multibib}
\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}
\newcites{preprints,published}{{Preprints and submitted}, {Published}}
\newcommand{\sc}{\scshape}

\renewcommand{\labelitemi}{-}


\usepackage{hyperref}

\name{Alexander}{Elzenaar}
\email{alexander.elzenaar@monash.edu}
\homepage{https://aelzenaar.github.io}
\social[orcid]{0000-0002-3047-8529}
\extrainfo{he/him}

\begin{document}

\makecvtitle


\section{Research interests}
\cvlistitem{Groups related to geometry and topology in low dimensions. Kleinian groups and their deformation theory; other aspects of geometric group theory, conformal geometry, and 3-manifold theory.
Applications of techniques from representation theory and algebraic geometry.}
\cvlistitem{Exemplar MSC codes: 20F65, 20H10, 22E40, 30F40, 30F60, 32G15, 51F15, 57K31, 57K32.}

\section{Tertiary education}
\cventry{2024--ongoing}{Doctoral student, geometry and topology}{School of Mathematics, Monash University}{Melbourne, Australia}{}{Advisor: Prof. Jessica Purcell. \newline{} Expected completion: 2027.}
\cventry{2021--2022}{MSc with First Class Honours in mathematics}{Dept. of Mathematics, The University of Auckland}{Auckland, NZ}{}{Advisors: Dist. Prof. Gaven Martin (NZ Inst. Adv. Study., Massey Uni.) and Dr. Jeroen Schillewaert. \newline{} Thesis: \textit{Deformation spaces of Kleinian groups} (\url{https://aelzenaar.github.io/msc_thesis.pdf}) }
\cventry{2020}{BSc (Hons) with First Class Honours in mathematics}{Dept. of Mathematics, The University of Auckland}{Auckland, NZ}{}{Advisor: Dr. Jeroen Schillewaert. \newline{} Dissertation: \textit{Toric varieties} (\url{https://aelzenaar.github.io/hons/dissertation.pdf})}
\cventry{awarded 2020}{Certificate of Languages}{School of Cultures, Languages and Linguistics, The University of Auckland}{Auckland, NZ}{}{Russian and Ancient Egyptian}
\cventry{2017--2019}{BSc, major in mathematics}{The University of Auckland}{Auckland, NZ}{}{}
\cventry{2016}{STAR programme}{The University of Canterbury}{Christchurch, NZ}{}{Distance learning first year university mathematics for secondary school students}

\section{Employment history (research)}
\cventry{2023--2024}{Research and data analyst, Evidence \& Insights branch}{Ministry of Business, Innovation, and Employment}{Wellington, NZ}{}{Mathematical modelling and statistics to support ministerial offices and policy evaluators
with particular focus in carbon modelling and econometric forecasting for the building and construction industry,
including production and peer review of departmental research output.}
\cventry{2022--2023}{Doctoral student}{Max-Planck-Inst. für Math. in den Naturwissenschaften}{Leipzig, Germany}{}{Non-linear algebra group. Withdrew for personal reasons.}
\cventry{2020--2021}{Research assistant}{Dept. of Mathematics, The University of Auckland}{Auckland, NZ}{}{
\begin{itemize}
\item Construction and symmetry properties of spherical $ (t,t)$-designs (funded by Dr.~Shayne~Waldron)
\item Teaching of semester-long graduate seminar on Kleinian groups (funded by Dr.~Jeroen~Schillewaert)
\end{itemize}}

\section{Employment history (teaching)}
\cventry{2025--2026}{Sessional teaching associate}{School of Mathematics, Monash University}{Melbourne, Australia}{}{
\begin{itemize}
  \item Tutoring and marking MAT~1030 (service calculus), sem. 1, 2026
  \item Tutoring and marking MAT~1020 (service calculus), sem. 1, 2025
\end{itemize}}
\cventry{2019--2022}{Graduate teaching assistant}{Dept. of Mathematics, The University of Auckland}{Auckland, NZ}{}{
\begin{itemize}
\item
Marking MATHS~208 (multivariate calculus service course), summer sem., 2022
\item
Tutoring \& marking MATHS~332 (real analysis); tutoring MATHS~190 (general education course), sem. 2, 2021
\item
Tutoring \& marking MATHS~250 (calculus \& linear algebra II); tutoring COMPSCI~225 (discrete mathematics for CS); marking MATHS~254 (number theory; groups; metric spaces), sem. 1, 2021
\item
Tutoring \& marking MATHS~190 (general education course); tutoring MATHS~120 (linear algebra); marking MATHS~340 (real \& complex calculus), sem. 2, 2020
\item
Tutoring MATHS~162 (computational mathematics \& combinatorics); assistance room tutor; marking MATHS~120 (linear algebra), MATHS~130 (calculus), COMPSCI~120 (mathematics for CS), sem. 1, 2020
\item
Marking MATHS~253 (calculus \& linear algebra III), sem. 2, 2019
\end{itemize}}
\cventry{2017--2019}{Secondary school tutor}{MyTuition}{Auckland, NZ}{}{Mathematics, physics, chemistry, geography}


\section{Awards and scholarships}

\cvitem{Program associate fellowship, SLMath}{\href{https://www.slmath.org/programs/368}{Topological and Geometric Structures in Low Dimensions Program} (Jan. to Mar. 2026)}
\cvitem{\href{https://carmamaths.org/art/gallery/competition/}{CARMA-MATRIX Maths Art Poster Competition}}{first prize in the outreach category for \href{https://aelzenaar.github.io/cones/poster_2025.pdf}{\textit{Fractals that parameterise hyperbolic handlebodies}} (2025)}
\cvitem{\href{https://www.monash.edu/study/fees-scholarships/scholarships/find-a-scholarship/research-training-program-scholarship}{Research Training Program Scholarship and Stipend (Australian Govt.)}}{tenure 2024--2027}
\cvitem{Clay Mathematics Institute Early Career Researcher Support}{for attendance of \href{https://sites.google.com/view/nzmri2023}{NZMRI Summer School on Groups and Dynamics, Nelson} (2023)}
\cvitem{Kalman Summer Scholarship}{for attendance of \href{https://www.math.canterbury.ac.nz/~f.voloch/nzmri.html}{NZMRI summer meeting on number theory, Akaroa} (2022)}
\cvitem{Uni. of Auckland Dept. of Mathematics Student Research Conference prize}{(2021)}
\cvitem{Kalman Summer Scholarship}{for attendance of \href{https://www.math.auckland.ac.nz/~conder/NZMRI-Napier-2021/}{NZMRI summer meeting, Napier} (2021)}
\cvitem{Uni. of Auckland Postgraduate Honours Scholarship}{tenure 2020}
\cvitem{Uni. of Auckland Summer Research Scholarship}{for \href{https://aelzenaar.github.io/tight_frames/scholarship_report.pdf}{\textit{Numerical construction of spherical $ (t,t)$-designs}} with Dr. Shayne Waldron (2019)}
\cvitem{Uni. of Auckland Faculty of Arts Dean's List}{(2017)}
\cvitem{\href{https://web.archive.org/web/20170211162000/http://www.nzqa.govt.nz/about-us/news/2016-outstanding-scholar-award-winners}{NZQA Outstanding Scholar Award}}{Limited to top 40--60 secondary school students in New Zealand, including an Outstanding Scholarship in Classical Studies (one of 13 awarded nationally) (2016)}
\cvitem{Royal Society of New Zealand scholarship}{to attend \href{https://web.archive.org/web/20161023213407/http://www.math.bas.bg/omi/hssimi/}{XVI Summer Research School in Mathematics and Informatics}, Blagoevgrad, Bulgaria (2016)}

\section{Academic works}
\nocitepreprints{*}
\bibliographystylepreprints{aomplainxxx}
\bibliographypreprints{preprints}

\nocitepublished{*}
\bibliographystylepublished{aomplainxxx}
\bibliographypublished{published}

\section{Selected talks}

\cvlistitem{``Quantifying shape and position of discreteness loci in $\mathsf{PSL}(2,\mathbb{C})$''\!, \href{https://www.slmath.org/programs/368}{Postgraduate seminar, Topological and Geometric Structures in Low Dimensions} (SLMath, Berkeley), 13 March 2026.}
\cvlistitem{``Generalised Ford domains arising from peripheral geometry''\!, \href{https://www.austms2025.org.au/}{ 69th Annual Meeting of the Australian Mathematical Society} (La Trobe Uni.), 9 December 2025.}
\cvlistitem{``What do knots have to do with algebra?''\!, \href{https://www.ivvy.com.au/event/COTEX6/home.html}{2025 NZMS Colloquium} (Uni. of Waikato), 27 November 2025.}
\cvlistitem{``Discontinuous subgroups of come in real-algebraic families with stable combinatorics''\!, \href{https://9thaac.github.io/}{9th Australian Algebra Conference} (La Trobe Uni.), 18 November 2025.}
\cvlistitem{``Cone manifolds and compression bodies''\!, Topology Seminar (Monash Uni.) 22 October 2025.}
\cvlistitem{``Deformations of 3-orbifold holonomy groups and applications''\!, Early Career Showcase in Low-Dimensional Topology, \href{https://ms-meet-2024.blogs.auckland.ac.nz/}{Joint Meeting of the NZMS, AustMS, and AMS} (Uni. of Auckland), 11 December 2024.}
\cvlistitem{``Combinatorial structures in trace polynomials of function groups''\!, \href{https://maths.anu.edu.au/news-events/events/8th-australian-algebra-conference}{8th Australian Algebra Conference} (ANU, Canberra), 28 November 2024.}
\cvlistitem{``Two-bridge knots, genus two surfaces, and discrete groups with two generators''\!, \href{https://sites.google.com/view/agtw/hodgsonfest}{Hodgsonfest: Geometry and topology in low dimensions} (Uni. Melbourne) 12 November 2024.}
\cvlistitem{``Is $ \mathsf{PSL}(2,\mathbb{C}) $ discrete?''\!, Topology Seminar (Monash Uni.) 24 July 2024.}
\cvlistitem{``The dynamic in the static: Manifolds, braids, and classical number theory''\!, \href{https://sites.google.com/view/regiomontanus-phd/}{Regiomontanus PhD Seminar} (Uni. Leipzig), 10 May 2023.}
\cvlistitem{``What is a Kleinian group?''\!, \href{https://www.apacmath.org}{Australian Postgraduate Algebra Colloquium}, 21 September 2022.}
\cvlistitem{``Pictures of hyperbolic spaces''\!, \href{https://www.mi.fu-berlin.de/en/math/groups/discgeom/index.html}{Discrete Mathematics and Geometry Seminar} (TU Berlin), 4 May 2022.}
\cvlistitem{``Strange circles: The Riley slice of quasi-Fuchsian space''\!, \href{https://www.mis.mpg.de/events/series/seminar-on-nonlinear-algebra}{Seminar on Nonlinear Algebra} (MPI MiS), 27 April 2022.}
\cvlistitem{``Approximating the Riley slice exterior''\!, \href{https://www.matrix-inst.org.au/events/groups-and-geometries/}{Matrix Inst. workshop on Groups and Geometries}, 2 December 2021.}
\cvlistitem{``Some properties of $2 \times 2 $ matrices''\!, Dept. of Mathematics Student Research Conference (Uni. of Auckland), 8 June 2021.}
\cvlistitem{``Real varieties of spherical designs''\!, Algebra and Combinatorics Seminar (Uni. of Auckland), 1 April 2021.}

\section{Professional service}
\cvlistitem{Refereeing for scholarly publications.}
\cvlistitem{Reviewing for \href{https://zbmath.org/?q=rn:21835}{zbMATH Open}.}

\subsection{Selected events organised}
\cvlistitem{\href{https://aelzenaar.github.io/\#knots23}{Minicourse on knot theory and geometry} (Uni. Auckland), including guest lectures by Lavender Marshall and Josh Lehman (July 2023).}
\cvlistitem{Reproducibility in Computer Algebra event (MPI-MiS/TU Berlin), co-organised with Christiane G\"orgen and Lars Kastner (August 2022).}
\cvlistitem{\href{https://aelzenaar.github.io/\#lorentzian_day}{A Day of Geometry and Lorentzian Polynomials} (MPI-MiS), single day of short informal talks in preparation for \href{https://www.mittag-leffler.se/activities/goran-gustafsson-symposium/}{Göran Gustafsson Symposium} at the Institut Mittag-Leffler (May 2022).}
\cvlistitem{Seminar on Kleinian groups (Uni. Auckland), weekly lectures covering approximately the first half of \textit{Kleinian Groups} by B. Maskit along with some sections of Thurston's lecture notes and the book \textit{Hyperbolic Manifolds and Discrete Groups} by M. Kapovich. Funded by Jeroen Schillewaert through a Research Assistantship (2021).}
\cvlistitem{Reading group on algebraic geometry (Uni. Auckland), jointly organised with Oliver Li (2020--2021).}


\section{Professional affiliations}
\cvlistitem{\href{http://nzmathsoc.org.nz/}{New Zealand Mathematical Society}, Student member}
\cvlistitem{\href{https://austms.org.au}{Australian Mathematical Society}, Student member}


\section{References}
Teaching and research reference letters available on request.

\vfill\hfill [\today]

\end{document}
