% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CV.tex
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[a4paper,yyyy,nonstopmode,10pt]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

\usepackage{amsmath,amssymb}
% \usepackage[T1]{fontenc}
% \usepackage{fontspec}
\usepackage{microtype}
% \usepackage{unicode-math}
% \setmainfont{STIXTwoText}[Extension=.otf,
%     UprightFont=*-Regular,
%     BoldFont=*-Bold,
%     ItalicFont=*-Italic,
%     BoldItalicFont=*-BoldItalic]
% \setmathfont{STIXTwoMath-Regular}[Extension=.otf]

\usepackage{cprotect}
\usepackage{xcolor}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Alexander Elzenaar}
\newcommand{\CVTitle}{Curriculum Vitae}
\newcommand{\CVNote}{\today}
\newcommand{\CVWebpage}{https://aelzenaar.github.io/}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
\href{mailto:alexander.elzenaar@monash.edu}
{alexander.elzenaar@monash.edu}
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{\CVWebpage}}
% \,\SubBulletSymbol\,
% \href{https://orcid.org/0000-0002-3047-8529}{ORCiD 0000-0002-3047-8529}
\,\SubBulletSymbol\,
he/him
\end{SubTitle}

\begin{Body}

\Section
{Research interests}
{Research interests}
{PDF:ResearchInterests}

\BulletItem Groups related to geometry and topology in low dimensions. Kleinian groups and their deformation theory; other aspects of geometric group theory, conformal geometry, and 3-manifold theory.
Applications of techniques from representation theory and algebraic geometry. Some computational work, particularly related to visualisation.

\BulletItem Exemplar MSC codes: 20F65, 20H10, 22E40, 30F40, 30F60, 32G15, 51F15, 57K31, 57K32.

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Research \& teaching positions}
{Research and teaching positions}
{PDF:ResearchExperience}

\Entry
\href{https://www.monash.edu/science/schools/school-of-mathematics}
{School of Mathematics, \textbf{Monash University}}, Melbourne,
Australia

\Gap
\BulletItem
Sessional teaching associate
\hfill
\DatestampY{2025}
\begin{Detail}
\SubBulletItem
Tutoring and marking MAT~1020 (calculus service course for non-mathematicians) \hfill Sem. 1 \DatestampY{2025}
\end{Detail}

\Entry
\href{https://mbie.govt.nz/}
{\textbf{Ministry of Business, Innovation, and Employment}},
Wellington, New Zealand
\Gap
\BulletItem
Research and data analyst, Evidence \& Insights branch
\hfill
\DatestampYM{2023}{9}--\DatestampYM{2024}{4}
\begin{Detail}
\SubBulletItem
Mathematical modelling and statistics to support ministerial offices and policy evaluators
with particular focus in carbon modelling and econometric forecasting for the building and construction industry,
including production and peer review of departmental research output.
\end{Detail}

\Entry
\href{https://www.mis.mpg.de/institute.html}
{\textbf{Max-Planck-Institut für Mathematik in den Naturwissenschaften}}, Leipzig, Germany
\Gap
\BulletItem
Doctoral student (withdrew), combinatorial algebraic geometry
\hfill\DatestampYM{2022}{4}--\DatestampYM{2023}{6}

\Entry
\href{http://www.auckland.ac.nz/}
{Dept. of Mathematics, \textbf{The University of Auckland}},
New Zealand

\Gap
\BulletItem
Research assistant (Professional Casual Staff)
\hfill
\DatestampY{2020}--\DatestampY{2021}
\begin{Detail}
\SubBulletItem
Construction and symmetry properties of spherical $ (t,t)$-designs (funded by Dr.~Shayne~Waldron)
\SubBulletItem
Teaching of semester-long graduate seminar on Kleinian groups (funded by Dr.~Jeroen~Schillewaert)
\end{Detail}

\Gap
\BulletItem
Graduate Teaching Assistant (GTA)
\hfill
\DatestampY{2019}--\DatestampY{2022}
\begin{Detail}
\SubBulletItem
Marking MATHS~208 (multivariate calculus service course) \hfill Summer sem. \DatestampY{2022}
\SubBulletItem
Tutoring \& marking MATHS~332 (real analysis); tutoring MATHS~190 (general education course) \hfill Sem. 2 \DatestampY{2021}
\SubBulletItem
Tutoring \& marking MATHS~250 (calculus \& linear algebra II); tutoring COMPSCI~225 (discrete mathematics for CS); marking MATHS~254 (elementary number theory; groups; metric spaces) \hfill Sem. 1 \DatestampY{2021}
\SubBulletItem
Tutoring \& marking MATHS~190 (general education course); tutoring MATHS~120 (linear algebra); marking MATHS~340 (real \& complex calculus) \hfill Sem. 2 \DatestampY{2020}
\SubBulletItem
Tutoring MATHS~162 (computational mathematics \& combinatorics); assistance room tutor; marking MATHS~120 (linear algebra), MATHS~130 (calculus), COMPSCI~120 (mathematics for CS) \hfill Sem. 1 \DatestampY{2020}
\SubBulletItem
Marking MATHS~253 (calculus \& linear algebra III) \hfill Sem. 2 \DatestampY{2019}
\end{Detail}


%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Tertiary Education}
{Tertiary Education}
{PDF:Education}

\Entry
\href{http://monash.edu.au/}
{\textbf{Monash University}},
Melbourne, Australia

\Gap
\BulletItem
(Ongoing) PhD candidate, Geometry and topology
\hfill
Likely completion 2027
\begin{Detail}
\SubBulletItem
Advisor: Prof. Jessica Purcell
\end{Detail}

\Entry
\href{http://www.auckland.ac.nz/}
{\textbf{The University of Auckland}},
New Zealand

\Gap
\BulletItem
Master of Science with First Class Honours in
\href{http://math.auckland.ac.nz/}
{mathematics}
\hfill
\DatestampYM{2021}{02}--\DatestampYM{2022}{2}
\begin{Detail}
\SubBulletItem
Thesis:
\textit{Deformation spaces of Kleinian groups} (\url{https://aelzenaar.github.io/msc_thesis.pdf})
\SubBulletItem
Advisors:
Dist.~Prof.~Gaven~Martin (NZ Inst. of Adv. Study, Massey Uni.),
Dr.~Jeroen~Schillewaert
\end{Detail}

\Gap
\BulletItem
Bachelor of Science (Hons) with First Class Honours
in
\href{http://math.auckland.ac.nz/}
{mathematics}
\hfill
\DatestampYMD{2020}{12}{18}
\begin{Detail}
\SubBulletItem
Dissertation:
\textit{Toric varieties} (\url{https://aelzenaar.github.io/hons/dissertation.pdf})
\SubBulletItem
Advisor:
Dr.~Jeroen~Schillewaert
\end{Detail}

\Gap
\BulletItem
Certificate in Languages
\hfill
awarded \DatestampY{2020}
\begin{Detail}
\SubBulletItem
Russian and Ancient Egyptian
\end{Detail}

\Gap
\BulletItem
Bachelor of Science, major in
\href{http://math.auckland.ac.nz/}
{mathematics}
\hfill
\DatestampY{2017}--\DatestampY{2019}
\begin{Detail}
% \SubBulletItem
% Until early 2019, I was enrolled in a conjoint Mathematics (BA)/Physics (BSc) degree
\SubBulletItem
Exchange student at the University of Toronto, 2018 fall semester
\end{Detail}

\Entry
\href{http://www.canterbury.ac.nz/}
{\textbf{The University of Canterbury}},
New Zealand

\Gap
\BulletItem
\href{https://www.canterbury.ac.nz/get-started/transition/star-programme/}
{STAR programme}
\hfill
\DatestampY{2016}
\begin{Detail}
\SubBulletItem
First year university mathematics program for secondary school students
\end{Detail}

% \Entry
% \textbf{Upper Hutt College}, New Zealand
% \Gap
% \BulletItem
% NCEA Level 3 with excellence endorsement and University Entrance certificate
% \hfill
% \DatestampY{2016}
% \begin{Detail}
% \SubBulletItem
% Chemistry, English, Geography, Mathematics with Calculus, Mathematics with Statistics, Physics
% \end{Detail}



%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards, \newline
Grants, \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}


\Gap
\BulletItem
AustMS Student Support Scheme
\hfill
\DatestampY{2024}
\begin{Detail}
\SubBulletItem
for attendance of \href{https://ms-meet-2024.blogs.auckland.ac.nz/}{Joint Meeting of the NZMS, AustMS, and AMS in Auckland}
\end{Detail}

\Gap
\BulletItem
Institute for Mathematical Sciences (Singapore) travel allowance
\hfill
\DatestampY{2024}
\begin{Detail}
\SubBulletItem
for attendance of program \href{https://ims.nus.edu.sg/events/computational-aspects-of-thin-groups/}{\textit{Computational Aspects of Thin Groups}} (3--14 June)
\end{Detail}

\Gap
\BulletItem
\href{https://www.monash.edu/study/fees-scholarships/scholarships/find-a-scholarship/research-training-program-scholarship}{Research Training Program (RTP) Stipend} (Australian Government)
\hfill
ongoing from \DatestampY{2024}

\Gap
\BulletItem
Clay Mathematics Institute Early Career Researcher Support
\hfill
\DatestampY{2023}
\begin{Detail}
\SubBulletItem
for attendance of \href{https://sites.google.com/view/nzmri2023}{NZMRI Summer School on Groups and Dynamics, Nelson}
\end{Detail}

\Gap
\BulletItem
Kalman Summer Scholarship
\hfill
\DatestampY{2022}
\begin{Detail}
\SubBulletItem
for attendance of \href{https://www.math.canterbury.ac.nz/~f.voloch/nzmri.html}{NZMRI summer meeting on number theory, Akaroa}
\end{Detail}

\Gap
\BulletItem
University of Auckland Department of Mathematics Student Research Conference prize
\hfill
\DatestampY{2021}

\Gap
\BulletItem
Kalman Summer Scholarship
\hfill
\DatestampY{2021}
\begin{Detail}
\SubBulletItem
for attendance of \href{https://www.math.auckland.ac.nz/~conder/NZMRI-Napier-2021/}{NZMRI summer meeting, Napier}
\end{Detail}

\Gap
\BulletItem
University of Auckland Postgraduate Honours / PG Diploma Scholarship
\hfill
\DatestampY{2020}

\Gap
\BulletItem
University of Auckland Summer Research Scholarship
\hfill
\DatestampYMD{2019}{12}{01}--\DatestampYMD{2020}{02}{29}
\begin{Detail}
\SubBulletItem
Project: \href{https://aelzenaar.github.io/tight_frames/scholarship_report.pdf}{Numerical construction of spherical $ (t,t)$-designs}
\SubBulletItem
Advisor:
Dr.~Shayne~Waldron
\end{Detail}

\Gap
\BulletItem
University of Auckland Faculty of Arts Deans List
\hfill
\DatestampY{2017}

\Gap
\BulletItem
\href{https://web.archive.org/web/20170211162000/http://www.nzqa.govt.nz/about-us/news/2016-outstanding-scholar-award-winners}{NZQA Outstanding Scholar Award}
\hfill
\DatestampY{2016}
\begin{Detail}
\SubBulletItem
Limited to top 40--60 secondary school students in New Zealand
% \SubBulletItem
% Outstanding Scholarship in Classical Studies; Scholarship in Chemistry, Geography, Mathematics with Calculus (also won in 2015), and Physics
% \Gap
% \BulletItem
% Dux, Upper Hutt College
% \hfill
% \DatestampY{2016}
%
\end{Detail}
\Gap
\BulletItem
Royal Society of New Zealand scholarship
\hfill
\DatestampY{2016}
\begin{Detail}
\SubBulletItem
to attend \href{https://web.archive.org/web/20161023213407/http://www.math.bas.bg/omi/hssimi/}{XVI Summer Research School in Mathematics and Informatics}, Blagoevgrad, Bulgaria
\end{Detail}



%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\Section
{Preprints \& submitted}
{Publications and submitted}
{PDF:Preprints}


% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[88]}

\BigGap
\NumberedItem{[9]}
\underline{A.~Elzenaar}, ``Peripheral subgroups of Kleinian groups''.\\{\small\color{black!70}\href{https://arxiv.org/abs/2508.00297}{arXiv: 2508.00297} [math.GT],
\DatestampYM{2025}{08}.}
\Gap
\NumberedItem{[8]}
\underline{A.~Elzenaar}, ``From disc patterns in the plane to character varieties of knot groups''.\\{\small\color{black!70}\href{https://arxiv.org/abs/2503.13829}{arXiv: 2503.13829} [math.GT],
\DatestampYM{2025}{03}.}
\Gap
\NumberedItem{[7]}
\underline{A.~Elzenaar}, ``Changing topological type of compression bodies through cone manifolds''.\\{\small\color{black!70}\href{https://arxiv.org/abs/2411.17940}{arXiv: 2411.17940} [math.GT],
\DatestampYM{2024}{12}.}
\Gap
\NumberedItem{[6]}
\underline{A.~Elzenaar}, G.~Martin, and J.~Schillewaert, ``On thin Heckoid and generalised triangle groups in $\mathsf{PSL}(2,\mathbb{C}) $''.\\{\small\color{black!70}\href{https://arxiv.org/abs/2409.04438}{arXiv: 2409.04438} [math.GR],
\DatestampYM{2024}{09}.}
\Gap
\NumberedItem{[5]}
\underline{A.~Elzenaar}, J.~Gong, G.~Martin, and J.~Schillewaert,
``Bounding deformation spaces of 2-generator Kleinian groups''.\\{\small\color{black!70}
\href{https://arxiv.org/abs/2405.15970}{arXiv: 2405.15970} [math.CV],
\DatestampYM{2024}{05}.}

\endgroup

\Section
{Publications}
{Publications}
{PDF:Publications}


% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[88]}

\NumberedItem{[4]}
\underline{A.~Elzenaar} and S.~Waldron,
``Putatively optimal projective spherical designs with little apparent symmetry''. In: \textit{Journal of Combinatorial Designs} \textbf{33}.6 (2025), pp.~222--234.\\{\small\color{black!70}\cprotect{\href{https://doi.org/10.1002/jcd.21979}}{DOI: \verb|10.1002/jcd.21979|}. \href{https://arxiv.org/abs/2405.19353}{arXiv: 2405.19353} [math.CO],
\DatestampYM{2024}{05}.}
\Gap
\NumberedItem{[3]}
\underline{A.~Elzenaar}, G.~Martin, and J.~Schillewaert,
``The combinatorics of the Farey words and their traces''. In: \textit{Groups, Geometry and Dynamics} (2024), published online first.\\{\small\color{black!70}\cprotect{\href{https://doi.org/10.4171/GGD/832}}{DOI: \verb|10.4171/GGD/832|}. \href{https://arxiv.org/abs/2204.08076}{arXiv: 2204.08076} [math.GT],
\DatestampYM{2022}{04}.}
\Gap
\NumberedItem{[2]}
\underline{A.~Elzenaar}, G.~Martin, and J.~Schillewaert,
``Concrete one complex dimensional moduli spaces of hyperbolic manifolds and orbifolds''. In: \textit{2021-22 MATRIX annals}. Ed. by David R. Wood, Jan de Gier, and Cheryl E. Prager. MATRIX Book Series 5. Springer, 2024,
pp.~31--74.\\{\small\color{black!70}\cprotect{\href{https://doi.org/10.1007/978-3-031-47417-0_2}}{DOI: \verb|10.1007/978-3-031-47417-0_2|}. \href{https://arxiv.org/abs/2204.08076}{arXiv: 2204.11422} [math.GT],
\DatestampYM{2022}{04}.}
\Gap
\NumberedItem{[1]}
\underline{A.~Elzenaar}, G.~Martin, and J.~Schillewaert,
``Approximations of the Riley slice''. In: \textit{Expositiones Mathematicae} \textbf{41}.1 (2023), pp.~20--54.\\{\small\color{black!70}\href{https://doi.org/10.1016/j.exmath.2022.12.002
}{DOI: 10.1016/j.exmath.2022.12.002}. \href{https://arxiv.org/abs/2111.03230}{arXiv: 2111.03230} [math.GT],
\DatestampYM{2021}{11}}

\endgroup


%%%%%%%%%%%
%% TALKS %%
%%%%%%%%%%%

\Section
{Selected\\talks}
{Selected talks}
{PDF:Talks}


% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[88]}

\BigGap
\NumberedItem{[12]}
``Deformations of 3-orbifold holonomy groups and applications'', Early Career Showcase in Low-Dimensional Topology, \href{https://ms-meet-2024.blogs.auckland.ac.nz/}{Joint Meeting of the NZMS, AustMS, and AMS} (Uni. of Auckland),
\DatestampYM{2024}{12}.
\Gap
\NumberedItem{[11]}
``Limit sets of cone manifolds'', Poster session, \href{https://ms-meet-2024.blogs.auckland.ac.nz/}{Joint Meeting of the NZMS, AustMS, and AMS} (Uni. of Auckland),
\DatestampYM{2024}{12}.
\Gap
\NumberedItem{[10]}
``Combinatorial structures in trace polynomials of function groups'', \href{https://maths.anu.edu.au/news-events/events/8th-australian-algebra-conference}{8th Australian Algebra Conference} (ANU, Canberra),
\DatestampYM{2024}{11}.
\Gap
\NumberedItem{[9]}
``Two-bridge knots, genus two surfaces, and discrete groups with two generators'', \href{https://sites.google.com/view/agtw/hodgsonfest}{Hodgsonfest: Geometry and topology in low dimensions} (Uni. Melbourne),
\DatestampYM{2024}{11}.
\Gap
\NumberedItem{[8]}
``Is $ \mathsf{PSL}(2,\mathbb{C}) $ discrete?'', Topology Seminar (Monash Uni.),
\DatestampYM{2024}{07}.
\Gap
\NumberedItem{[7]}
``The dynamic in the static: Manifolds, braids, and classical number theory'', \href{https://sites.google.com/view/regiomontanus-phd/}{Regiomontanus PhD Seminar} (Uni. Leipzig),
\DatestampYM{2023}{05}.
\Gap
\NumberedItem{[6]}
``What is a Kleinian group?'', \href{https://www.apacmath.org}{Australian Postgraduate Algebra Colloquium},
\DatestampYM{2022}{09}.
\Gap
\NumberedItem{[5]}
``Pictures of hyperbolic spaces'', \href{https://www.mi.fu-berlin.de/en/math/groups/discgeom/index.html}{Discrete Mathematics and Geometry Seminar} (TU Berlin),
\DatestampYM{2022}{05}.
\Gap
\NumberedItem{[4]}
``Strange circles: The Riley slice of quasi-Fuchsian space'', \href{https://www.mis.mpg.de/events/series/seminar-on-nonlinear-algebra}{Seminar on Nonlinear Algebra} (MPI MiS),
\DatestampYM{2022}{04}.
\Gap
\NumberedItem{[3]}
``Approximating the Riley slice exterior'', \href{https://www.matrix-inst.org.au/events/groups-and-geometries/}{Matrix Inst. workshop on Groups and Geometries},
\DatestampYM{2021}{12}.
\Gap
\NumberedItem{[2]}
``Some properties of $2 \times 2 $ matrices'', Dept. of Mathematics Student Research Conference (Uni. of Auckland),
\DatestampYM{2021}{06}.
\Gap
\NumberedItem{[1]}
``Real varieties of spherical designs'', Algebra and Combinatorics Seminar (Uni. of Auckland),
\DatestampYM{2021}{04}.

\endgroup


%%%%%%%%%%%%%%%
%% ORGANISED %%
%%%%%%%%%%%%%%%

\Section
{Events\\(co-)organised}
{Evrnts (co-)organised}
{PDF:Events}


% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[88]}

\BigGap
\NumberedItem{[8]}
Guest lectures for MATHS 782 ``Geometric Group Theory'' (Uni. Auckland),
\DatestampYM{2024}{07}.
\begin{Detail}
\SubBulletItem
Two hours of lectures invited by Jeroen Schillewaert in the first week of a graduate course to provide a `preview' of basic geometric and topological ideas e.g. quotients by discrete groups and hyperbolic geometry.
\end{Detail}
\Gap
\NumberedItem{[7]}
\href{https://aelzenaar.github.io/#knots23}{Minicourse on knot theory and geometry} (Uni. Auckland),
\DatestampYM{2023}{07}.
\begin{Detail}
\SubBulletItem
Eight 2-hour lectures at the University of Auckland, aimed at graduate students in geometric group theory.
\SubBulletItem
Six lectures were given by me, and two honours students at Auckland (Lavender Marshall and Josh Lehman) were invited to give talks related to their work.
\href{https://aelzenaar.github.io/#knots23}{Lecture notes} for the entire course were produced by me.
\end{Detail}
\Gap
\NumberedItem{[6]}
Minicourse on deformation theory of Kleinian groups (MPI and Uni. Auckland),
\DatestampYM{2022}{12}, \DatestampYM{2023}{01}.
\begin{Detail}
\SubBulletItem
One afternoon workshop at MPI, with the purpose of trying to open a dialog with tropical geometers about the links between moduli of tropical varieties and graph curves, and the deformation theory of Kleinian groups.
\SubBulletItem
Three 2-hour lectures at the University of Auckland subsequent to the \href{https://sites.google.com/view/nzmri2023}{NZMRI Summer School on Groups and Dynamics, Nelson}.
\SubBulletItem
Produced expository note \href{https://aelzenaar.github.io/kg/ephemera/ephemera.pdf}{Apocrypha and ephemera on the boundaries of moduli space}, outlining intuition and rough background
for a programme of work to study geometrically finite Kleinian groups using the ideas of Keen, Series, Akiyoshi, and others. This document is superceeded by more detailed work currently
being finalised.
\end{Detail}
\Gap
\NumberedItem{[5]}
Uniformisation of Riemann surfaces workshop afternoon (MPI),
\DatestampYM{2022}{10}.
\begin{Detail}
\SubBulletItem
Produced expository note \href{https://aelzenaar.github.io/riemann/riemann.pdf}{Uniformisation, equivariance, and vanishing---Three kinds of functions hanging around your Riemann surface}.
\end{Detail}
\Gap
\NumberedItem{[4]}
Reproducibility in Computer Algebra event (MPI/TU Berlin),
\DatestampYM{2022}{08}.
\begin{Detail}
\SubBulletItem
Co-organised with Christiane G\"orgen and Lars Kastner.
\end{Detail}
\Gap
\NumberedItem{[3]}
\href{https://aelzenaar.github.io/#lorentzian_day}{A Day of Geometry and Lorentzian Polynomials} (MPI),
\DatestampYM{2022}{05}.
\begin{Detail}
\SubBulletItem
Sole organiser, single day of short informal talks in preparation for \href{https://www.mittag-leffler.se/activities/goran-gustafsson-symposium/}{Göran Gustafsson Symposium} at the Institut Mittag-Leffler (May 2022).
\end{Detail}
\Gap
\NumberedItem{[2]}
Seminar on Kleinian groups (Uni. Auckland),
\DatestampYM{2021}{01}--\DatestampYM{2021}{08}.
\begin{Detail}
\SubBulletItem
Gave two 2-hour lectures per week, covering approximately the first half of \textit{Kleinian Groups} by B. Maskit along some sections of Thurston's lecture notes and the book \textit{Hyperbolic Manifolds and Discrete Groups}
by M. Kapovich.
\SubBulletItem
Organised with financial support of Jeroen Schillewaert who employed me as a Research Assistant for the purpose of giving these lectures to introduce his buildings research group to the theory
of Kleinian groups. Jeroen also gave a couple of guest lectures. The majority of preparation work (e.g. determining syllabus, finding suitable sources to draw from, writing
lecture notes) was done by me.
\end{Detail}
\Gap
\NumberedItem{[1]}
Reading group in Algebraic Geometry (Uni. Auckland),
\DatestampY{2019}--\DatestampY{2020}.
\begin{Detail}
\SubBulletItem
Co-organised with Oliver Li, which involved organising other honours students to produce lectures, initially following sections of Hartshorne's introductory textbook and then later more specialised sources related to honours projects.
\end{Detail}
\endgroup

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL AFFILIATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Professional Affiliations}
{Professional Affiliations}
{PDF:ProfessionalAffiliationsActivities}

\Gap
\Entry
\href{http://nzmathsoc.org.nz/}
{\textbf{New Zealand Mathematical Society}},
Student member
\Gap
\Entry
\href{https://austms.org.au}
{\textbf{Australian Mathematical Society}},
Student member

% Manual page break.
% \newpage

%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

\Section
{References}
{References}
{PDF:References}

Teaching and research reference letters available on request.


\end{Body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\BigGap
\UseNoteFont%
\null\hfill%
[\textit{\CVNote}]

\end{document}
